Methodology for Assessing the State of the Practice for Domain X

### 2020-04-15 StateOfPractice/Methodology/GradingTemplate.tex
more comments to the grading template

\begin{longtable}{p{16cm}}
  \caption{Grading Template}   \label{table:TemplateFull}\\
  \toprule
  \textbf{Summary Information}\\
  \midrule
  Software name? (string)\\
  URL? (url)\\
  Educational institution (string)\\
  Software purpose (string)\\
  Number of developers (number)\ad{It might be hard to decide. For example 3D Slicer has 171 people with commits to its repo, but on its website, 18 contributors(including people who are not developers) are acknowledged.}\\
  How is the project funded (string)\\
  Number of downloads for current version (number)\\
  Release date (date)\\
  Last updated (date)\\
  Status (\{alive, dead, unclear\})\\
  License (\{GNU GPL, BSD, MIT, terms of use, trial, none, unclear\})\\
  Platforms (set of \{Windows, Linux, OS X, Android, Other OS\})\\
  Category (\{concept, public, private\})\\
  Development model (\{open source, freeware, commercial\})\\
  Publications using the software (set of url)\\
  Publications about the software (set of url) \\
  Is source code available? (\{yes, no\})\ad{It might be better to directly ask for a set of url, and the answer can be n/a if it's not open source, or unclear if it can't be determined.}\\
  Source code URL (\{set of url, n/a, unclear\})\ad{example}\\
  Programming language(s) (set of \{FORTRAN, Matlab, C, \CC, Java, R, Ruby,
  Python, Cython, BASIC, Pascal, IDL, unclear\})\\

@@

  Is there a history of multiple versions of the software?  (\{yes, no, unclear\})\\
  Is there any information on how code is reviewed, or how to contribute?
  (\{yes$^*$, no\})\\
  Is there a changelog?  (\{yes, no\})\\
  What is the maintenance type? (set of \{corrective, adaptive, perfective, unclear\})\\
  What issue tracking tool is employed? (set of \{Trac, JIRA, Redmine, e-mail,
  discussion board, sourceforge, google code, git, none, unclear\}) \ad{Does git mean GitHub and GitLab? Should we add BitBucket here?}\\
  Are the majority of identified bugs fixed? (\{yes, no$^*$, unclear\})\ad{It might be better to record a number here}\\
  What is the percentage of identified issues that are closed? (percentage)\ad{an example}\\
  Which version control system is in use? (\{svn, cvs, git, github, unclear\})\\
  Is there evidence that maintainability was considered in the design?
  (\{yes$^*$, no\})\\
  Are there code clones? (\{yes$^*$, no, unclear\})\ad{Might need to test some static analyzer.}\\
  Overall impression? (\{1 .. 10\})\\

@@

  What platforms is the software advertised to work on?
  (set of \{Windows, Linux, OS X, Android, Other OS\})\\
  Are special steps taken in the source code to handle portability? (\{yes$^*$,
  no, n/a\}) \\
  Is portability explicitly identified as NOT being important? (\{yes, no\})\\
  Convincing evidence that portability has been achieved? (\{yes$^*$, no\})\\
  Overall impression? (\{1 .. 10\})\\

@@

  Consistent indentation and formatting style? (\{yes, no, n/a\})\\
  Explicit identification of a coding standard? (\{yes$^*$, no, n/a\})\\
  Are the code identifiers consistent, distinctive, and
  meaningful? (\{yes, no$^*$, n/a\})\\
  Are constants (other than 0 and 1) hard coded into the program? (\{yes, no$^*$, n/a\})\\
  Comments are clear, indicate what is being done, not how? (\{yes, no$^*$, n/a\})\\
  Is the name/URL of any algorithms used mentioned?
  (\{yes, no$^*$, n/a\})\\
  Parameters are in the same order for all functions? (\{yes, no$^*$, n/a\})\\
  Is code modularized? (\{yes, no$^*$, n/a\})\\
  Descriptive names of source code files? (\{yes, no$^*$, n/a\})\\
  Is a design document provided? (\{yes$^*$, no, n/a\})\\
  Overall impression? (\{1 .. 10\})\\

@@

  Does the software interoperate with external systems? (\{yes$^*$, no\})\\
  Is there a workflow that uses other softwares? (\{yes$^*$, no\})\\
  If there are external interactions, is the API clearly defined? (\{yes$^*$, no, n/a\})\\
  Overall impression? (\{1 .. 10\})\\

@@

  Is the development process defined? If yes, what process is used. (\{yes$^*$, no, n/a\})\\
  Ease of external examination relative to other products
  considered?  (\{1 .. 10\})\\
  Overall impression? (\{1 .. 10\})\\

>>>>

\begin{longtable}{p{16cm}}
  \caption{Grading Template}   \label{table:TemplateFull}\\
  \toprule
  \textbf{Summary Information}\\
  \midrule
  Software name? (string)\\
  URL? (url)\\
  Educational institution (string)\\
  Software purpose (string)\\
  Number of developers (number)\ad{It might be hard to decide. For example 3D Slicer has 171 people with commits to its repo, but on its website, 18 contributors(including people who are not developers) are acknowledged.}\\
  How is the project funded (string)\\
  Number of downloads for current version (number)\\
  Release date (date)\\
  Last updated (date)\\
  Status (\{alive, dead, unclear\})\\
  License (\{GNU GPL, BSD, MIT, terms of use, trial, none, unclear\})\\
  Platforms (set of \{Windows, Linux, OS X, Android, Other OS\})\\
  Category (\{concept, public, private\})\\
  Development model (\{open source, freeware, commercial\})\\
  Publications using the software (set of url)\\
  Publications about the software (set of url) \\
  Is source code available? (\{yes, no\})\ad{It might be better to directly ask for a set of url, and the answer can be n/a if it's not open source, or unclear if it can't be determined. An example is as follows.}\\
  \ad{Example}Source code URL (\{set of url, n/a, unclear\})\\
  Programming language(s) (set of \{FORTRAN, Matlab, C, \CC, Java, R, Ruby,
  Python, Cython, BASIC, Pascal, IDL, unclear\})\\

@@

  Is there a history of multiple versions of the software?  (\{yes, no, unclear\})\\
  Is there any information on how code is reviewed, or how to contribute?
  (\{yes$^*$, no\})\\
  Is there a changelog?  (\{yes, no\})\\
  What is the maintenance type? (set of \{corrective, adaptive, perfective, unclear\})\\
  What issue tracking tool is employed? (set of \{Trac, JIRA, Redmine, e-mail,
  discussion board, sourceforge, google code, git, none, unclear\}) \ad{Does git mean GitHub and GitLab? Should we add BitBucket here?}\\
  Are the majority of identified bugs fixed? (\{yes, no$^*$, unclear\})\ad{It might be better to record a number here. An example is as follows.}\\
  \ad{Example}What is the percentage of identified issues that are closed? (percentage)\\
  Which version control system is in use? (\{svn, cvs, git, github, unclear\})\\
  Is there evidence that maintainability was considered in the design?
  (\{yes$^*$, no\})\\
  Are there code clones? (\{yes$^*$, no, unclear\})\ad{Might need to test some static analyzer.}\\
  Overall impression? (\{1 .. 10\})\\

@@

  What platforms is the software advertised to work on?
  (set of \{Windows, Linux, OS X, Android, Other OS\})\\
  Are special steps taken in the source code to handle portability? (\{yes$^*$,
  no, n/a\}) \\
  Is portability explicitly identified as NOT being important? (\{yes, no\})\\
  Convincing evidence that portability has been achieved? (\{yes$^*$, no\})\ad{Seems like a good question to put in the questionnaire}\\
  Overall impression? (\{1 .. 10\})\\

@@

  Consistent indentation and formatting style? (\{yes, no, n/a\})\\
  Explicit identification of a coding standard? (\{yes$^*$, no, n/a\})\\
  Are the code identifiers consistent, distinctive, and
  meaningful? (\{yes, no$^*$, n/a\})\\
  Are constants (other than 0 and 1) hard coded into the program? (\{yes, no$^*$, n/a\})\\
  Comments are clear, indicate what is being done, not how? (\{yes, no$^*$, n/a\})\\
  Is the name/URL of any algorithms used mentioned?
  (\{yes, no$^*$, n/a\})\\
  Parameters are in the same order for all functions? (\{yes, no$^*$, n/a\})\\
  Is code modularized? (\{yes, no$^*$, n/a\})\\
  Descriptive names of source code files? (\{yes, no$^*$, n/a\})\\
  Is a design document provided? (\{yes$^*$, no, n/a\})\ad{What is a design document? There can be some examples.}\\
  Overall impression? (\{1 .. 10\})\\

@@

  Does the software interoperate with external systems? (\{yes$^*$, no\})\\
  Is there a workflow that uses other softwares? (\{yes$^*$, no\})\\
  If there are external interactions, is the API clearly defined? (\{yes$^*$, no, n/a\})\\
  \ad{Some more suggested questions are as follows:}\\
  \ad{1.}Can the output be used by other software as input?(\{yes$^*$, no\})\\
  \ad{2.}Can it take output from other software as input?(\{yes$^*$, no\})\\
  \ad{3.}Does the software generate output files with uncommon formats or extensions? Such as the ones that can only be used by itself.(\{yes$^*$, no, n/a\})\\
  \ad{4.}Can the software work with customized plug-ins? (\{yes, no\})\\
  Overall impression? (\{1 .. 10\})\\

@@

  Is the development process defined? If yes, what process is used. (\{yes$^*$, no, n/a\})\ad{Seems like a good question to put in the questionnaire}\\
  Ease of external examination relative to other products
  considered?  (\{1 .. 10\})\\
  \ad{Some more suggested questions are as follows:}\\
  \ad{1.}Are there any documents recording the development process and status? (\{yes$^*$, no,\})\\
  \ad{2.}Are there release notes? (\{yes, no\})\\
  \ad{3.}In the issue tracking system, are there at least some issues assigned to specific developers? (\{yes, no\})\ad{It would be better to get a percentage, but the empirical tool can't achieve this. It might be worth to manually count the most recent 50 issues.}\\
  \ad{4.}In the issue tracking system, are there at least some issues with tags of types and priorities? (\{yes, no\})\ad{In GitHub, tags are optional. In BitBucket, it seems to be mandatory. In SourceForge, it seems to be not supported.}\\
  \ad{5.}Are there any project management tools used during the development?\ad{Seems like a good question to put in the questionnaire}\\
  Overall impression? (\{1 .. 10\})\\
